%
% File: chap01.tex
% Author: Wesley Hoffman
% Description: Introduction and Welcome
%
\let\textcircled=\pgftextcircled
\chapter{Introduction}
\label{chap:intro}

\initial{W}elcome to the first edition of the University of Kansas ACM Student
Chapter Handbook. This will be your guide on how to best run the ACM Student
Chapter as a member of the Executive Board, herein referred to as the Board, and
ensure its success for now and the years ahead. This handbook is to be passed down
to each new executive board and can be edited and revised as seen fit. However,
this should not apply to official parent organization guidelines, governance,
and bylaws. This chapter has a short history, but it is comprised of very proud
and passionate individuals. Hopefully, these tidbits on the lessons and rules we
learned will help you avoid and learn from our mistakes.

%=======
\section{Name}
\label{sec:sec01}

This organization shall be called the University of Kansas at Lawrence Student
Chapter of the Association for Computing Machinery, herein referred to as ACM@KU.
The parent organization, the Association for Computing Machinery, is herein
referred to as the Association. All affiliated Special Interest Groups are herein
referred to as SIGs. This organization may officially be referred to by any of
the following terms:
\begin{itemize}
  \item ACM@KU
  \item Association for Computing Machinery at Lawrence
  \item University of Kansas at Lawrence Student Chapter of the Association for
        Computing Machinery
\end{itemize}

\section{Introduction to Being a Board Member}
\label{sec:sec02}

% Question for Wes
%
% Does the faculty sponsor, as defined as an "Officer" (previously Core Officer)
% need to be present to remove an officer???

Each Board member is to be responsible for their duties outlined in the following
subsections. Clear communication between one another invokes a good understanding.
If for any reason a Board member cannot fulfill their duties, other Board members
may be delegated to support them until said Board member can resume their
responsibilities. Additional Board positions may be added or removed as need be,
including SIG leaders, event coordinators, et cetera. However, the Officers
- defined below - must be present, as dictated by the Association and the Student
Involvement & Leadership Center, herein referred to as SILC. These are not
removable positions.
\begin{itemize}
  \item ACM@KU shall have four official officer positions, herein referred to as
        the Officers, to represent the organization:
        Chair, Vice Chair, Treasurer, and Secretary.
  \item The Officers will be elected each March (maybe moving to December) in a
        specially designated election meeting chosen and publicized in good faith
        by the Board and run by the Chair or by his or her appointed representative.
  \item No Officer may hold more than one office in ACM@KU simultaneously.
  \item All Officers must, upon election, become members of the Association for
        Computing Machinery International.
\end{itemize}

\subsection{Officers}
\label{subsec:subsec01}

\begin{itemize}
  \item Chair
  \item Vice Chair
  \item Secretary
  \item Treasurer
  \item Faculty Sponsor
\end{itemize}

\subsection{Board Positions}
\label{subsec:subsec02}

\begin{itemize}
  \item Engineering Student Council Representative
  \item Publicity Director
  \item Programming Club Chair
  \item Web Master
\end{itemize}

%=========================================================
